---
title: "RLadies Hands on Data Session"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Introduction

2017 The State of Data Science & Machine Learning (Kaggle)

“This year, for the first time, we conducted an industry-wide survey to establish a comprehensive view of the state of data science and machine learning. We received over 16,000 responses and learned a ton about who is working with data, what’s happening at the cutting edge of machine learning across industries, and how new data scientists can best break into the field”.

## Useful references 

* Introduction to the problem: https://www.kaggle.com/surveys/2017 
* Examples: 
    * https://www.kaggle.com/amberthomas/kaggle-2017-survey-results

# Getting started 
## Load any libraries required for the analysis 

```{r load_libraries}
library(tidyverse)
```

## Import the data 

```{r import_data}
# Import multiple choice data
rawMCData <- read_csv('data/multipleChoiceResponses.csv')

# Import freeform responses
rawFFData <- read_csv('data/freeformResponses.csv')

# Import the actual questions asked
schema <- read_csv('data/schema.csv')

# Conversion rates 
conversionRates <- read_csv('data/conversionRates.csv')
```

## View the data 
Below are different ways to initially explore the data to get started.  

```{r view_the_data}
head(rawMCData)
glimpse(rawFFData)
summary(conversionRates)
```

TEST 2